Resources for Data-Driven Search-Based Software Engineering

### 2018-01-19 doc/tex/msr18/main.tex
Restructuring

\maketitle
\pagestyle{plain}
% \input{samplebody-conf}
\section{Introduction}
The Mining Software Repositories (MSR) community has benefited enormously from widely shared data sets.  Such data sets document the canonical problems in a field.
They serve to cluster together like-minded researchers while also
  allowing   them to generate reproducible results. Further, they can be used by
   newcomers to learn state-of-the-set methods in this field. Finally, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.

>>>>

\maketitle
\pagestyle{plain}
% \input{samplebody-conf}
\section{Introduction}
This paper initiates a new shared resource for the Mining Software
Repositories (MSR) community.
Fig1 shows the Github repoistory \href{ai-se/ResourcesDataDrivenSBSE}{https://github.com/ai-se/ResourceDataDrivenSBSE}. In this report we descibe the why and
what of this resource. Our intent is that, as a result
of this paper, we receive many pull requests that extend
this repository into a useful resource for   MSR.

The MSR  community has benefited enormously from widely shared data sets.  Such data sets document the canonical problems in a field.
They serve to cluster together like-minded researchers while also
  allowing   them to generate reproducible results. Further, they can be used by
   newcomers to learn state-of-the-set methods in this field. Finally, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
